Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-06 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-06 16-22-54

In this type of ``fixed'' - ``adaptive'' architecture, the mathematical formulation is not clear.
Moreover, if the partial shading part is large enough to cover ``adaptive'' part, this scheme become ineffective.
\section{Conclusion}
The conclusion goes here.

>>>>

In this type of ``fixed'' - ``adaptive'' architecture, the mathematical formulation is not clear.
Moreover, if the partial shading part is large enough to cover ``adaptive'' part, this scheme become ineffective.
Velasco $et$ $al.$\cite{Velasco-Quesada2009,velasco2008grid,velasco2005energy} proposed an principle of operation is referred as ``irradiance equalization''.
Reconfiguration strategy based on this principle aim to relocate the PV panels on the rows so that ``irradiance equalization'' is achieved.
However, optimal configuration requires differences between ``row'' irradiance level are minimized as shown in \cite{Velasco-Quesada2009} therefore it can only be realized on fully reconfigurable array.
They proposed algorithm that calculate all possible configurations and stored as look-up table locally.
Then, the ``best'' configuration for real-time shading scenario will be chosen from look-up table.
There is no doubt that the number of possible configurations will increase from the size of the PV array and it will be more difficult to determine the optimal configuration with limited time.
\section{Conclusion}
The conclusion goes here.
